\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{changepage}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large Alberto Morón Hernández} \\
    \vspace{12pt}
    \href{mailto:alberto.moronh@gmail.com}alberto.moronh@gmail.com
     \hspace{42pt}
     \href{https://www.albertomh.com}{\color{blue}\underline{albertomh.com}}
     \hspace{42pt}
    \href{https://github.com/albertomh/}{\color{blue}\underline{github.com/albertomh}}
\end{center}

%-----------SUMMARY-----------
%\vspace{3pt}
\begin{adjustwidth}{0.15in}{0.15in}
Commercially-minded software engineer at ease across the stack and at home in cross-functional teams. Keen on robust APIs, DevOps practices and ensuring all disciplines have a seat at the table. I use automation \& consistency to enable teams to focus on delivery.
\end{adjustwidth}

%----------- SKILLS-----------
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL (Postgres), Bash, TypeScript, Java} \\
     \textbf{Frameworks}{: FastAPI, Pydantic, SQLAlchemy, Alembic, Django, pytest, Selenium, React, Angular} \\
     \textbf{Tools}{: Git, Docker, GitLab pipelines \& GitHub Actions, Terraform, Google Cloud, make/just, pre-commit} \\
     \textbf{Methodologies}{: peer review, Agile, DevOps, CI/CD, IaC, trunk-based flow, release automation} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{Sep 2022 -- present}
      {University of Cambridge}{Cambridge \& remote, UK}
      \vspace{0pt}
    \resumeItemListStart
        \resumeItem{Collaborate with Product Managers, User Researchers, Business Analysts and fellow engineers on data-driven \& cloud-first services that enable Cambridge's admissions process.}
        \resumeItem{Build observability into services and use real data to inform impactful changes: both broad (product roadmaps) \& targeted (performance improvements).}
        \resumeItem{Use Agile methods to discover user needs and iterate on effective ways of working with stakeholders.}
        \resumeItem{Build and maintain APIs that are testable, ergonomic, scalable and secure.}
        \resumeItem{Write and peer-review code across the stack: Python (FastAPI, Django), Terraform (Google Cloud), Bash \& YAML (pipelines), TypeScript (React).}
        \resumeItem{Adopt DevOps practices: containers, IaC, GitLab CI/CD, automation, monitoring, 12-Factor.}
        \resumeItem{Co-lead interviews for software engineers.}
    \resumeItemListEnd
      \vspace{4pt}

    \resumeSubheading
      {Software Engineer}{Feb 2019 -- Apr 2022}
      {Wealth Club}{Bristol, UK}
      \vspace{0pt}
    \resumeItemListStart
        \resumeItem{Enabled flagship site to grow 94\% YoY and handle 10x traffic spikes. Made it 3.5x cheaper to run and increased SEO score with serverless Cloudflare Workers.}
        \resumeItem{Reduced costs: performed attribution modelling to understand clients' response to marketing campaigns and halved the monthly CDN bill by refactoring to alternatives within Cloudflare.}
        \resumeItem{Analysed and visualised investment data with Python \& JavaScript: numpy, pandas, D3.js.}
        \resumeItem{Co-led interviews for software engineers \& testers. Mentored two junior colleagues.}
    \resumeItemListEnd
      \vspace{4pt}

    \resumeSubheading
      {Junior Developer}{Jun 2017 -- Feb 2019}
      {Nomensa}{Bristol, UK}
      \vspace{0pt}
    \resumeItemListStart
        \resumeItem{Part of a team of UX researchers, designers, and developers building a learning platform for the NHS.}
        \resumeItem{Pioneered JavaScript service workers to enable the webapp to work offline inside operating theatres.}
        \resumeItem{Created data visualisation \& forecasting tools in Python (numpy, matplotlib) to monitor application health, provide insights into user behaviour and inform the product roadmap.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Manchester}{2014 - 2017}
      {B.A., Linguistics -- First Class Honours}{Manchester, UK}
      \vspace{0pt}
      \begin{adjustwidth}{0in}{0in}
       \small Research on paraphrasing verbal metonymy via computational methods supported by an Amazon Educate grant.
      2017 Q-Step Prize for best quantitative dissertation. \href{https://arxiv.org/abs/1709.06162}arxiv.org/abs/1709.06162
      \end{adjustwidth}
  \resumeSubHeadingListEnd

\vspace{-6pt}

  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Massachusetts, Amherst}{2016}
      {Computational Linguistics -- 3.8/4.0 GPA, Dean’s List}{Massachusetts, USA}
  \resumeSubHeadingListEnd
\end{document}
